Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-19 Paper.tex
Rewording

Note that $\mindifficulty$ is the difficulty of the genesis block. The effect of the difficulty parameter $\homesteadmod$ on a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. $\expdiffsymb$ results in the difficulty increasing every 10000 blocks. This is necessary to stabilise the time difference between blocks as  computation power becomes more efficient, with Moore's Law, although the rate of increase in computational efficiency has slowed down and may probably continue to slow down (\cite{THOMPSON200620}.

>>>>

Note that $\mindifficulty$ is the difficulty of the genesis block. The difficulty parameter $\homesteadmod$ is used to affect a dynamic homeostasis of time between blocks, as the time between blocks varies, as discussed below. $\expdiffsymb$ results in the difficulty increasing every 10000 blocks. This is necessary to stabilise the time difference between blocks as  computation power becomes more efficient, with Moore's Law, although the rate of increase in computational efficiency has slowed down and may probably continue to slow down (\cite{THOMPSON200620}.
